Measuring the Price of Anarchy in Critical Care Unit Interactions

### 2014-12-18 Paper/paper.tex
Adding the fact that LoS follows patient
Adding bibtex files

The effect of state dependent service rates in healthcare has been well studied in isolated hospitals.
In \cite{A} an empirical study is undertaken and service rate slow down is identified.
Furthermore, it is shown that modelling whilst ignoring these state dependent rates leads to errors.
This effect is further identified in \cite{B,C} where for example the negative effect on patient outcome is revealed.
In \cite{D,E} this is expanded to consider a variety of admission policies in two CCUs, in particular the effect of rejection (due to too high occupancy) is measured.
These policies are studied in the setting of a single hospital, and thus, from a game theoretic \cite{Maschler2013} point of view correspond to rational behaviour.
In practice a simplification of rational strategies is managed by policy makers by setting utilisation targets that ensure that hospitals do not run at a level likely to have a high rejection rate (example of these can be seen \cite{Bevan2006, url1, url2}).

@@

\begin{itemize}
    \item The assumptions as to the strategy space of our players is restrictive: a single threshold policy might not be optimal (although it is present in various pieces of literature on optimal control of queueing systems: \cite{naor1969regulation, shone2013comparisons});
    \item This model only assumes the presence of two players however in reality the system has a variety of stakeholders. Multi player systems could be worth considering;
    \item The restriction to pure strategies is influenced by discussions with ABUHB and also does not detract from the results presented thanks to the Theorem and Lemma of Section \ref{queueingandgamemodels}.  However, allowing for mixed strategies could also be of interest.
\end{itemize}

>>>>

The effect of state dependent service rates in healthcare has been well studied in isolated hospitals.
In \cite{batt2012doctors} an empirical study is undertaken and service rate slow down is identified.
Furthermore, it is shown that modelling whilst ignoring these state dependent rates leads to errors.
This effect is further identified in \cite{chan2014use, kc2012econometric} where for example the negative effect on patient outcome is revealed.
In \cite{kim2013icu, shmueli2003optimizing} this is expanded to consider a variety of admission policies in two CCUs, in particular the effect of rejection (due to too high occupancy) is measured.
These policies are studied in the setting of a single hospital, and thus, from a game theoretic \cite{Maschler2013} point of view correspond to rational behaviour.
In practice a simplification of rational strategies is managed by policy makers by setting utilisation targets that ensure that hospitals do not run at a level likely to have a high rejection rate (example of these can be seen in \cite{Bevan2006, NHS2013}).

@@

\begin{itemize}
    \item The assumptions as to the strategy space of our players is restrictive: a single threshold policy might not be optimal (although it is present in various pieces of literature on optimal control of queueing systems: \cite{naor1969regulation, shone2013comparisons});
    \item This model only assumes the presence of two players however in reality the system has a variety of stakeholders. Multi player systems could be worth considering;
    \item The restriction to pure strategies is influenced by discussions with ABUHB and also does not detract from the results presented thanks to the Theorem and Lemma of Section \ref{queueingandgamemodels}.  However, allowing for mixed strategies could also be of interest.
    \item Patient length of stay is assumed to be dependent on the CCU at which they receive service. A further extension of the work would be to use the service rate from original CCU (prior to diversion). This would require a Markov chain with a higher dimensional state space.
\end{itemize}
